PANCHANGE_analysis

### 2020-09-17 PANCHANGE_analysis.Rmd

@@

>>>>

### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model absolute values absolute values 0a}
gad_prepan_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

Model 0b: Overlapping disorders, Unadjusted
```{r GAD prepan Model absolute values 0b}
gad_prepan_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1a}
gad_prepan_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1b}
gad_prepan_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model absolute values 0a}
phq_prepan_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model absolute values 0b}
phq_prepan_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1a}
phq_prepan_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1b}
phq_prepan_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model absolute values 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model absolute values 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model absolute values 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model absolute values 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model absolute values 0a}
gad_retro_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model absolute values 0b}
gad_retro_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1a}
gad_retro_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1b}
gad_retro_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model absolute values 0a}
phq_retro_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model absolute values 0b}
phq_retro_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1a}
phq_retro_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1b}
phq_retro_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model absolute values 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model absolute values 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model absolute values 0a}
ocir_retro_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model absolute values 0b}
ocir_retro_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1a}
ocir_retro_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1b}
ocir_retro_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)
